Challenges in Developing Great Quasi-Monte Carlo Software

### 2023-03-18 MCQMC2022ChallengesQMCSoftwareArticle.tex
sc: fix broken url with hyperref
sc: use hyperref with url

% RECOMMENDED %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[graybox]{svmult}

@@

%%%%Fred start
\input{common-macros.tex}
\usepackage{cite}
\usepackage{xspace}
\usepackage[hyphens]{url}
\providecommand{\HickernellFJ}{Hickernell\xspace}
\graphicspath{{ProgramsImages/}}

@@

Users computing solutions in comprehensive software environments, such as NAG, MATLAB, R, SciPy, and TensorFlow, have convenient access to LD sequence generators.  However, most of these implementations in large libraries would benefit a wider menu of LD offerings, including custom generators from LatNetBuilder or other sources.  Some large environments such as  Dakota \cite{DakotaUsersManual} have quite limited LD generators and should expand their offerings. SAS facilitates flexible integration of third-party open-source software; see \url{https://www.sas.com/en_us/software/viya/open.html}.
This presents opportunities for developers of smaller libraries with more QMC features, like BRODA and QMCPy, to connect their libraries with larger software environments. An example of QMCPy connecting with other software is given in the next subsection.

@@

The term research software engineer (RSE) is becoming a more valued vocation.  According to the website for  Research Software Engineers International, \url{https://researchsoftware.org}, \emph{Research Software Engineers are people who combine professional software expertise with an understanding of research.}

>>>>

% RECOMMENDED %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\PassOptionsToPackage{hyphens}{url}
\documentclass[graybox]{svmult}

@@

%%%%Fred start
\input{common-macros.tex}
\usepackage{cite}
\usepackage{xspace}
\usepackage[bookmarks=false]{hyperref}
\usepackage[hyphens]{url}
\providecommand{\HickernellFJ}{Hickernell\xspace}
\graphicspath{{ProgramsImages/}}

@@

Users computing solutions in comprehensive software environments, such as NAG, MATLAB, R, SciPy, and TensorFlow, have convenient access to LD sequence generators.  However, most of these implementations in large libraries would benefit a wider menu of LD offerings, including custom generators from LatNetBuilder or other sources.  Some large environments such as  Dakota \cite{DakotaUsersManual} have quite limited LD generators and should expand their offerings. SAS facilitates flexible integration of third-party open-source software; see \href{https://www.sas.com/en_us/software/viya/open.html}{\url{https://www.sas.com/en_us/software/viya/open.html}}.
This presents opportunities for developers of smaller libraries with more QMC features, like BRODA and QMCPy, to connect their libraries with larger software environments. An example of QMCPy connecting with other software is given in the next subsection.

@@

The term research software engineer (RSE) is becoming a more valued vocation.  According to the website for  Research Software Engineers International, 
\href{https://researchsoftware.org}{\url{https://researchsoftware.org}}, \emph{Research Software Engineers are people who combine professional software expertise with an understanding of research.}
